Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-20 draft.tex
typo and cite type change

When \citep{collberg:2014, collberg:2015} decided to measure the extent of the problem
precisely, they investigated the availability of code and data as well as {\em the extent to which this code would actually build with reasonable
  effort}. The results were dramatic: of the 515 (out of 613) potentially reproducible
papers targeted by the study, the authors managed to ultimately run
only 102 (i.e. less than 20\%). These low numbers figures reflect only the authors success at running the code. They did not check for correctness of the code (does the code actually implement what is advertised in the paper), nor the replicability of the results (does the run lead to the same results as in the paper).  \citep{topalidou:2015a} encountered the same
problem when they tried to replicate a model from the computational neuroscience literature: source code was not part of the supplementary section
of the paper and no link or repository was provided in the main text. When they
finally got their hands on the code, after contacting the corresponding
author, it was only to realize that it could not be compiled and was mostly
unusable.\\

>>>>

When \citep{collberg:2014, collberg:2015} decided to measure the extent of the problem
precisely, they investigated the availability of code and data as well as {\em the extent to which this code would actually build with reasonable
  effort}. The results were dramatic: of the 515 (out of 613) potentially reproducible
papers targeted by the study, the authors managed to ultimately run
only 102 (i.e. less than 20\%). These low numbers reflect only the authors success at running the code. They did not check for correctness of the code (does the code actually implement what is advertised in the paper), nor the replicability of the results (does the run lead to the same results as in the paper).  \citet{topalidou:2015a} encountered the same
problem when they tried to replicate a model from the computational neuroscience literature: source code was not part of the supplementary section
of the paper and no link or repository was provided in the main text. When they
finally got their hands on the code, after contacting the corresponding
author, it was only to realize that it could not be compiled and was mostly
unusable.\\
